% Created 2026-03-24 Tue 20:33
% Intended LaTeX compiler: pdflatex
\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\author{Pascal Bourguignon}
\date{2026-03-24}
\title{Reply Email Draft}
\hypersetup{
 pdfauthor={Pascal Bourguignon},
 pdftitle={Reply Email Draft},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 30.2 (Org mode 9.7.11)}, 
 pdflang={English}}
\begin{document}

\maketitle
Hi Jaimie, hi Kees,

Thank you for sharing the full Trinity Engine canon package.

I have now completed an in-depth review of the documents. I am attaching a written report with the detailed analysis, but I wanted to summarize the main conclusion here as well.

My overall assessment is that the package is strong enough to begin implementation work on most of the agreed deterministic scope. The architecture of the canon is thoughtful, the scope boundaries are much clearer than in earlier materials, and the Human Design mapping and structural rules are substantially more explicit than I would normally expect at this stage.

That said, I do see a small number of canon-critical points that should be clarified and folded back into the governing documents before final fixture freeze and acceptance review.

The main blockers I identified are:

\begin{enumerate}
\item The exact IANA Time Zone Database release is not pinned, even though timezone conversion can materially affect downstream deterministic results.
\item The house interval ownership rule for astrology house placement does not appear to be explicitly defined, especially for cusp-boundary behavior.
\item The Design time search method is well specified at a high level, but the canonical selection of the final timestamp at whole-second precision still needs to be pinned more explicitly.
\item The output contract defines error types, but not a canonical error message catalog or message construction rule, which makes exact error fixture matching under-specified.
\end{enumerate}

Beyond those, I also noted a few smaller but still important clarifications that would help remove interpretation risk:

\begin{enumerate}
\item The exact boundary between \texttt{invalid\_input} and \texttt{unsupported\_input} in some edge cases.
\item Whether IANA link or alias identifiers are acceptable as canonical timezone input.
\item How the first golden fixtures should be reviewed and approved so they are not simply self-frozen outputs from the implementation under test.
\item Whether success-response comparison is intended to be semantic JSON comparison or literal byte-for-byte serialized output.
\end{enumerate}

I have included the full list of ambiguities and concrete questions in the attached report.

So in short: I believe the package is close, and I believe implementation can begin in the clearly pinned areas now, but I would want the remaining canon-critical points above resolved explicitly rather than absorbed implicitly into code.

I’m looking forward to our call next week and to discussing this with you both.

Best regards,

Pascal
\end{document}
