% Created 2026-03-24 Tue 20:32
% Intended LaTeX compiler: pdflatex
\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\author{Pascal Bourguignon}
\date{2026-03-24}
\title{Trinity Engine Canon Review Report}
\hypersetup{
 pdfauthor={Pascal Bourguignon},
 pdftitle={Trinity Engine Canon Review Report},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 30.2 (Org mode 9.7.11)}, 
 pdflang={English}}
\begin{document}

\maketitle
\tableofcontents

\section{Executive Assessment}
\label{sec:orgb615176}
\begin{center}
\begin{tabular}{lll}
Question & Assessment & Summary\\
\hline
Is the canon complete enough to support implementation without interpretation? & No, not fully. & The package is unusually detailed and much stronger than a normal prose spec, but a few implementation-critical points still require interpretation.\\
Does ambiguity, conflict, or missing implementation-critical detail remain? & Yes. & The most important remaining gaps are timezone source version pinning, house interval ownership, design-time second-selection, and canonical error-message policy.\\
Is the package sufficient to begin deterministic implementation under the agreed scope? & Yes, with reservations. & Work can begin on most of the engine, but some areas should be treated as blocked until clarifications are folded back into the governing canon.\\
\end{tabular}
\end{center}

\begin{itemize}
\item High-level judgment:
\begin{itemize}
\item The package is strong enough to begin engineering work.
\item The package is not yet strong enough to claim a fully interpretation-free implementation.
\item The package is not yet strong enough to support final acceptance without clarifying a small number of critical issues.
\end{itemize}
\end{itemize}
\section{Strengths Of The Package}
\label{sec:org9f2447f}
\begin{itemize}
\item Scope is explicit and narrow.
\begin{itemize}
\item The package is disciplined about what is in scope and what is excluded.
\item The engine boundary is clear: normalized input only.
\end{itemize}
\item Core domain mechanics are substantially pinned.
\begin{itemize}
\item Human Design gate order, anchor, line width, center list, channel table, Type rules, and Authority priority are all explicitly formalized.
\item Astrology source stack, supported objects, sign mapping, and output structure are explicit.
\end{itemize}
\item Determinism governance is strong.
\begin{itemize}
\item Canon precedence, versioning, regression obligations, and no-hidden-state rules are unusually well documented.
\end{itemize}
\item Transparency is good.
\begin{itemize}
\item Document 09 and Document 12 make the decision history and prior rejected assumptions visible, which materially reduces hidden-context risk.
\end{itemize}
\end{itemize}
\section{Critical Ambiguities And Blockers}
\label{sec:org2fd350f}
\subsection{A1. Timezone Source Version Is Not Actually Pinned}
\label{sec:orga2b70bb}
\begin{itemize}
\item Documents:
\begin{itemize}
\item Document 03, section 3.2
\item Document 08, sections 4.3 and 6.4
\end{itemize}
\item Problem:
\begin{itemize}
\item The canon says the IANA Time Zone Database is authoritative, and Document 08 says source versions must be pinned where they affect outcomes.
\item However, no exact tzdb release is named anywhere in the reviewed package.
\end{itemize}
\item Why this matters:
\begin{itemize}
\item Historical DST rules do change across tzdb releases.
\item A different tzdb release can change UTC conversion, Julian Day, planetary positions, house cusps, and every downstream Human Design and Gene Keys result.
\end{itemize}
\item Assessment:
\begin{itemize}
\item This is implementation-critical.
\item A deterministic engine cannot be fully reproducible across environments without this pin.
\end{itemize}
\end{itemize}
\subsection{A2. House Interval Ownership Rules Are Missing}
\label{sec:orgdb81f56}
\begin{itemize}
\item Documents:
\begin{itemize}
\item Document 05, section 5.6
\item Document 06, section 3.4
\end{itemize}
\item Problem:
\begin{itemize}
\item Document 05 says house placement must follow "house interval rules defined elsewhere in the canon."
\item No governing document found in the reviewed package actually defines those interval rules.
\item The canon defines sign interval ownership and gate/line interval ownership, but not house interval ownership.
\end{itemize}
\item Why this matters:
\begin{itemize}
\item Every astrology object output requires a house value.
\item Without a canonical cusp-ownership rule, cusp-boundary cases can vary by implementation or by library convention.
\item This is especially important around wraparound between House 12 and House 1.
\end{itemize}
\item Assessment:
\begin{itemize}
\item This is a direct blocker for exact, interpretation-free astrology house assignment.
\end{itemize}
\end{itemize}
\subsection{A3. Design-Time Search Result Selection Is Underspecified At Whole-Second Precision}
\label{sec:orgd3652cd}
\begin{itemize}
\item Documents:
\begin{itemize}
\item Document 05, sections 6.4.5 through 6.4.7
\item Document 05, section 11.2
\item Document 07, sections 10.3 and 10.4
\end{itemize}
\item Problem:
\begin{itemize}
\item The canon pins bisection and the stop conditions.
\item It does not pin what timestamp is returned when stop condition 2 is met: "remaining interval width is less than 1 second."
\item It also does not pin whether emission to whole-second precision should use floor, ceiling, nearest, or another rule.
\end{itemize}
\item Why this matters:
\begin{itemize}
\item Human Design and Gene Keys outputs depend on \texttt{design\_time\_utc}.
\item A one-second difference can change gate or line at a boundary.
\item Two compliant-looking implementations could stop on different final bracket endpoints and emit different values.
\end{itemize}
\item Assessment:
\begin{itemize}
\item This is implementation-critical for exact fixtures and deterministic interoperability.
\end{itemize}
\end{itemize}
\subsection{A4. Canonical Error Messages Are Not Pinned}
\label{sec:org3ada4c6}
\begin{itemize}
\item Documents:
\begin{itemize}
\item Document 07, section 9.5
\item Document 10, section 6.3
\end{itemize}
\item Problem:
\begin{itemize}
\item Output Specification only says the message must be a machine-readable developer-facing string.
\item Golden Test Pack says exact message matching is preferred for v1.
\item No authoritative message catalog or message-construction rule was found.
\end{itemize}
\item Why this matters:
\begin{itemize}
\item If fixtures require exact message strings, the implementer must invent them.
\item That makes exact fixture matching depend on non-canonical wording choices.
\end{itemize}
\item Assessment:
\begin{itemize}
\item This is a blocker for exact error-fixture authoring unless the review process explicitly limits matching to \texttt{error\_type}.
\end{itemize}
\end{itemize}
\section{Significant But Potentially Non-Blocking Ambiguities}
\label{sec:org76c0736}
\subsection{A5. Unsupported Input Classification Is Not Fully Operationalized}
\label{sec:org80db8bc}
\begin{itemize}
\item Documents:
\begin{itemize}
\item Document 04, sections 6.2 and 11
\item Document 07, section 9.4
\item Document 10, section 9.3
\end{itemize}
\item Problem:
\begin{itemize}
\item The package clearly distinguishes \texttt{invalid\_input}, \texttt{incomplete\_input}, and \texttt{unsupported\_input}.
\item But the exact decision boundary for some cases remains loose.
\item Example: seconds in \texttt{birth\_time} are rejected, but section 6.2 says minute-level absence may be rejected as \texttt{IncompleteInput} or \texttt{UnsupportedInput} "according to the final error handling rules."
\end{itemize}
\item Why this matters:
\begin{itemize}
\item The implementation can still start, but some error classifications could drift.
\item Fixture authoring becomes inconsistent unless those cases are normalized.
\end{itemize}
\end{itemize}
\subsection{A6. Valid Timezone Identifier Set Is Not Tight Enough}
\label{sec:orgdba5557}
\begin{itemize}
\item Documents:
\begin{itemize}
\item Document 04, section 6.3
\item Document 03, section 3.2
\end{itemize}
\item Problem:
\begin{itemize}
\item The canon says the field must be an IANA timezone identifier and rejects abbreviations like \texttt{CET}.
\item It does not clearly state whether IANA link names and aliases such as \texttt{US/Eastern} are accepted if supplied directly.
\end{itemize}
\item Why this matters:
\begin{itemize}
\item Validation behavior can differ even when both implementations use IANA data.
\item This affects both input acceptance and historical time conversion.
\end{itemize}
\end{itemize}
\subsection{A7. Golden Fixture Bootstrap Is Methodologically Weak}
\label{sec:org9fdd768}
\begin{itemize}
\item Documents:
\begin{itemize}
\item Document 10, Appendix A
\item Document 12, decision D18
\end{itemize}
\item Problem:
\begin{itemize}
\item The implementer is expected to populate the first full fixture set from a "canon compliant engine run" and then freeze it.
\item That means the initial fixture oracle is produced by the same implementation under review unless an external review step exists.
\end{itemize}
\item Why this matters:
\begin{itemize}
\item Golden fixtures then enforce regression consistency, but they do not independently prove initial correctness.
\item The package is sufficient for regression discipline, but not by itself for first-principles truth establishment.
\end{itemize}
\item Assessment:
\begin{itemize}
\item This is more of an acceptance-process risk than a coding blocker, but it matters for review credibility.
\end{itemize}
\end{itemize}
\subsection{A8. The Canon Itself Admits The Final Consistency Pass Is Not Fully Folded Back}
\label{sec:orgebc8343}
\begin{itemize}
\item Documents:
\begin{itemize}
\item Document 00
\item Document 09 item O02
\end{itemize}
\item Problem:
\begin{itemize}
\item The package still records a pending fold-back/completeness step for Documents 05-07.
\item That means identifier hygiene and cross-document wording drift remain known risks.
\end{itemize}
\item Why this matters:
\begin{itemize}
\item An engineer can proceed, but should expect some late canon edits.
\end{itemize}
\end{itemize}
\section{Potential Conflict Or Tension Points}
\label{sec:orgaa11bb8}
\subsection{C1. "Byte For Byte" Exactness Versus Partially Unpinned Serialization}
\label{sec:org21510a3}
\begin{itemize}
\item Source context:
\begin{itemize}
\item Earlier email language emphasizes exact expected output "byte for byte."
\item Output Specification focuses on canonical structure, field presence, ordered arrays, and pinned numeric/date formatting.
\end{itemize}
\item Tension:
\begin{itemize}
\item The package does not fully pin object member order or a canonical JSON serializer.
\item Document 07 explicitly allows some serialization variation such as trailing zeros depending on implementation serialization.
\end{itemize}
\item Assessment:
\begin{itemize}
\item If review is semantic JSON comparison, this is fine.
\item If review is literal byte-level comparison, this remains under-specified.
\end{itemize}
\end{itemize}
\section{Readiness By Workstream}
\label{sec:org4a314fb}
\begin{center}
\begin{tabular}{lll}
Workstream & Readiness & Notes\\
\hline
Input validation & Ready & Strongest part of the canon.\\
Source stack setup & Partially ready & Swiss Ephemeris is pinned; timezone source version is not.\\
Astrology signs and object ordering & Ready & Sign mapping and object set/order are clear.\\
Astrology house placement & Blocked & House interval ownership is not pinned.\\
Human Design gate/line mapping & Ready & Gate order, widths, anchor, and interval rules are explicit.\\
Human Design structural derivation & Ready & Channels, centers, definition, Type, and Authority are formalized.\\
Gene Keys derivation & Ready & Scope is narrow and mapping is explicit.\\
Error handling & Partially ready & Error types are clear; exact messages are not.\\
Golden test scaffolding & Ready & Structure and coverage are defined.\\
Golden fixture truth establishment & Partially ready & First fixture population lacks an independent oracle.\\
\end{tabular}
\end{center}
\section{Overall Conclusion}
\label{sec:orgdacf36d}
\begin{itemize}
\item The package is good enough to start deterministic implementation of most of the agreed scope.
\item It is not good enough to promise a fully interpretation-free implementation from start to finish.
\item The missing details are relatively small in number, but they hit high-leverage areas:
\begin{itemize}
\item timezone conversion reproducibility
\item astrology house placement
\item design-time exact second selection
\item error-fixture exactness
\end{itemize}
\item My recommendation:
\begin{itemize}
\item begin implementation now for the clearly pinned areas
\item explicitly mark a few areas as blocked pending canon clarification
\item require the clarifications to be folded back into the governing canon before final fixture freeze and acceptance review
\end{itemize}
\end{itemize}
\section{Ambiguities List}
\label{sec:org9b531c1}
\begin{itemize}
\item Critical:
\begin{itemize}
\item exact IANA Time Zone Database release is not pinned
\item house interval ownership / cusp-boundary rule is not pinned
\item design-time search final timestamp selection and second-rounding rule are not pinned
\item canonical error messages are not pinned despite exact fixture ambitions
\end{itemize}
\item Significant:
\begin{itemize}
\item \texttt{unsupported\_input} versus \texttt{invalid\_input} boundary is not fully operationalized
\item acceptance policy for IANA aliases/link names is not explicit
\item first golden fixture oracle is not independent of the implementation
\item final consistency pass across Documents 05, 06, and 07 is not fully folded back
\end{itemize}
\item Moderate:
\begin{itemize}
\item if literal bytewise JSON comparison is still intended, serialization rules remain under-specified
\end{itemize}
\end{itemize}
\section{Questions For Jaimie / Canon Owner}
\label{sec:orgcbab2fd}
\begin{enumerate}
\item Which exact IANA Time Zone Database release is authoritative for v1?
\item What are the canonical house interval ownership rules for house placement?
\item When the design-time bisection stops with interval width under 1 second, which timestamp is canonical: lower bound, upper bound, midpoint, or nearest whole second?
\item What rounding rule is canonical for emitting \texttt{design\_time\_utc} at whole-second precision?
\item Is there an authoritative catalog of error messages, or should fixtures match only \texttt{error\_type} and not exact \texttt{message} text?
\item Are IANA alias/link identifiers such as \texttt{US/Eastern} valid if submitted directly, or are only canonical \texttt{Area/Location} zone names accepted?
\item Which exact scenarios are intended to produce \texttt{unsupported\_input} rather than \texttt{invalid\_input} in v1?
\item How should the first golden expected outputs be reviewed and approved so they are not merely self-frozen output from the implementation under test?
\item Is semantic JSON comparison acceptable for success fixtures, or is literal byte-for-byte serialized output still the intended acceptance basis?
\end{enumerate}
\section{Recommended Next Step}
\label{sec:orgd7602ae}
\begin{itemize}
\item Ask for canon clarification on questions 1-5 before finalizing house placement, timezone handling, design-time output emission, and error fixtures.
\item Proceed immediately with:
\begin{itemize}
\item input validation
\item source-stack pinning except tzdb release
\item astrology longitude/sign/object calculation
\item Human Design gate/line mapping
\item Human Design structural derivation
\item Gene Keys derivation
\item output shape and metadata scaffolding
\item golden test harness structure
\end{itemize}
\end{itemize}
\end{document}
